%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\definecolor{awesome}{HTML}{414141}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Adam H.}{Sparks}

\position{Senior Research Scientist, Bioeconomic Modeller}
\address{State of Western Australia, Department of Primary Industries
and Regional Development, Level 5, 1 Nash St., Perth WA, 6000}

\mobile{+61 (4) 15489422}
\email{\href{mailto:adam.sparks@dpird.wa.gov.au}{\nolinkurl{adam.sparks@dpird.wa.gov.au}}}
\homepage{adamhsparks.com}
\orcid{0000-0002-0061-8359}
\github{adamhsparks}
\twitter{adamhsparks}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}

\quote{I have demonstrated consistent success both in non-profit
international NGO and academic settings and have an extensive background
of experiences in working with diverse partners.}

\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------



% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {May 29, 2021}
    {Adam H. Sparks~~~·~~~Curriculum Vitae}
  {\thepage}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{professional-experience}{%
\section{Professional Experience}\label{professional-experience}}

\begin{cventries}
    \cventry{Senior Research Scientist, Bioeconomic Modeller}{State of Western Australia DPIRD}{Perth, Western Australia, AUS}{2021 – Current}{\begin{cvitems}
\item Conduct research in agricultural systems modelling and develop decision support system tools for growers and advisors
\end{cvitems}}
    \cventry{Associate Professor of Field Crops Pathology}{University of Southern Queensland}{Toowoomba, Queensland, AUS}{2016 – 2021}{\begin{cvitems}
\item Lead research group in developing plant disease models to support the Australian grains and cotton industries
\item Lead research that contributes to the development of broadacre crop fungicide decision support system tools, e.g. PowderyMildewMBM
\item Act as project manager for research projects spanning across research organisations
\item Develop R packages that provide access to Australian and global weather or climate data and to assist in plant pathology research
\item Work with the UN’s FAO in a capacity building role to help build agrometeorology and pest and disease capabilities in Cambodia
\end{cvitems}}
    \cventry{Scientist I, Plant Disease Management Specialist}{International Rice Research Institute (IRRI)}{Los Baños, Laguna, PHL}{2012 – 2015}{\begin{cvitems}
\item Led research group in conducting research to reduce yield losses in tropical rice due to pests and diseases
\item Used models to help evaluate impact and test rice crop management methodologies
\item Acted as project manager for research projects spanning across research organisations and countries
\item Co-directed the development of a country-wide rice monitoring system, the Philippine Rice Information System (PRISM), which uses geospatial, cloud-hosted and mobile device technologies to gather digital information
\item Modelled the effects of climate change on rice diseases
\end{cvitems}}
    \cventry{Post-Doctoral Fellow}{International Rice Research Institute (IRRI)}{Los Baños, Laguna, PHL}{2011 – 2012}{\begin{cvitems}
\item Linked plant disease models with geographic information systems to map model outputs for decision making
\item Conducted in-field experiments to develop pest and disease management programs
\end{cvitems}}
    \cventry{Post-Doctoral Research Associate}{Kansas State University}{Manhattan, Kansas, USA}{2010 – 2010}{\begin{cvitems}
\item Used bootstrapping methods to refit logistic regression model coefficients for wheat Fusarium head blight models using new and expanded data sets
\item Studied the use of ensemble models to predict wheat Fusarium head blight
\end{cvitems}}
    \cventry{Research Technologist}{University of Nebraska – Lincoln}{Lincoln, Nebraska, USA}{2002 – 2004}{}\vspace{-4.0mm}
    \cventry{Research Technician}{University of Nebraska – Lincoln}{Clay Center, Nebraska, USA}{2000 – 2003}{}\vspace{-4.0mm}
    \cventry{Assistant Director}{Purdue University}{West Lafayette, Indiana, USA}{1999 – 2000}{}\vspace{-4.0mm}
    \cventry{Research Technician}{Purdue University}{West Lafayette, Indiana, USA}{1997 – 1999}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{education-and-qualifications}{%
\section{Education and
Qualifications}\label{education-and-qualifications}}

\begin{cventries}
    \cventry{Ph.D. of Plant Pathology in Epidemiology and Ecology of Plant Pathogens}{Kansas State University}{Manhattan, KS, USA}{Dec. 2009}{\begin{cvitems}
\item Dissertation Title: ``Disease risk mapping with metamodels for coarse resolution predictors: global potato late blight risk now and under future climate conditions.''
\item Committee members: Drs. Karen A. Garrett (adviser), James P. Stack, Erick DeWolf and J. M. Shawn Hutchinson.
\end{cvitems}}
    \cventry{Graduate Certificate in Geographic Information Sciences}{Kansas State University}{Manhattan, KS, USA}{Dec. 2007}{}\vspace{-4.0mm}
    \cventry{B.S. of Agronomy in Soil and Crop Management}{Purdue University}{West Lafayette, IN, USA}{May 2000}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{related-professional-skills}{%
\section{Related Professional
Skills}\label{related-professional-skills}}

\hypertarget{programming-abilities}{%
\subsection{Programming Abilities}\label{programming-abilities}}

\begin{itemize}
\tightlist
\item
  Programming: R (author and maintain packages on CRAN)
\item
  Operating System: macOS, Unix/Linux (install and maintain Linux)
\item
  Others: Git, Docker, LaTeX, Markdown and RMarkdown
\end{itemize}

\hypertarget{software}{%
\subsection{Software}\label{software}}

\begin{itemize}
\tightlist
\item
  Statistical Software: R
\item
  Office Software Packages: Microsoft Office/365, LibreOffice and Google
  Suites
\item
  GIS Software: R, QGIS, ArcGIS
\end{itemize}

\hypertarget{publications}{%
\section{Publications}\label{publications}}

\hypertarget{selected-publications}{%
\subsection{Selected Publications}\label{selected-publications}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs_articles}{}
\leavevmode\vadjust pre{\hypertarget{ref-deSousa2020}{}}%
de Sousa, K., \textbf{Sparks, A.}, Ashmall, W., van Etten, J., \&
Solberg, S. Ø. (2020). Chirps: {API} client for the CHIRPS precipitation
data in {R}. \emph{The Journal of Open Source Software}, \emph{5}(51),
2419. \url{https://doi.org/10.21105/joss.02419}

\leavevmode\vadjust pre{\hypertarget{ref-khaliq_role_2020}{}}%
Khaliq, I., Fanning, J., Melloy, P., Galloway, J., Moore, K., Burrell,
D., \& \textbf{Sparks, A.} (2020). The role of conidia in the dispersal
of \emph{{Ascochyta} rabiei}. \emph{European Journal of Plant
Pathology}. \url{https://doi.org/10.1007/s10658-020-02126-2}

\leavevmode\vadjust pre{\hypertarget{ref-Purushotham2020}{}}%
Purushotham, N., Jones, A., Poudel, B., Nasim, J., Adorada, D.,
\textbf{Sparks, A.}, \ldots{} Vaghefi, N. (2020). Draft genome resource
for \emph{{Macrophomina} phaseolina} associated with charcoal rot in
sorghum. \emph{Molecular Plant-Microbe Interactions}, \emph{33}(5),
724--726.

\leavevmode\vadjust pre{\hypertarget{ref-cucak2019evaluation}{}}%
Čučak, M., \textbf{Sparks, A.}, de Andrade R., M., Kildea, S., Lambkin,
K., \& Fealy, R. (2019). Evaluation of the {{'}Irish Rules{'}}: The
potato late blight forecasting model and its operational use in the
{Republic of Ireland}. \emph{Agronomy}, \emph{9}(9), 515.
\url{https://doi.org/10.3390/agronomy9090515}

\leavevmode\vadjust pre{\hypertarget{ref-McCoy2019}{}}%
McCoy, A. G., Noel, Z., \textbf{Sparks, A.}, \& Chilvers, M. (2019).
{hagis}, an {R} package resource for pathotype analysis of
\emph{{Phytophthora} sojae} populations causing stem and root rot of
soybean. \emph{Molecular Plant-Microbe Interactions}, \emph{32}(12),
1574--1576.

\leavevmode\vadjust pre{\hypertarget{ref-Pede2019}{}}%
Pede, V. O., Barboza, G., \textbf{Sparks, A.}, \& McKinley, J. (2019).
The inequality-growth link revisited with spatial considerations: The
case of provinces in the {Philippines}. \emph{Journal of the Asia
Pacific Economy}, \emph{23}(3), 411--427.
\url{https://doi.org/10.1080/13547860.2018.1503765}

\leavevmode\vadjust pre{\hypertarget{ref-Savary2018}{}}%
Savary, S., Nelson, A. D., Djurle, A., Esker, P. D.,
\textbf{Sparks, A.}, Amorim, L., \ldots{} Willocquet, L. (2018).
Concepts, approaches, and avenues for modelling crop health and crop
losses. \emph{European Journal of Agronomy}, \emph{100}, 4--18.
\url{https://doi.org/10.1016/j.eja.2018.04.003}

\leavevmode\vadjust pre{\hypertarget{ref-Sparks2018}{}}%
\textbf{Sparks, A.} (2018). {nasapower}: {A NASA POWER} global
meteorology, surface solar energy and climatology data client for {R}.
\emph{Journal of Open Source Software}, \emph{3}, 1035.
\url{https://doi.org/10.21105/joss.01035}

\leavevmode\vadjust pre{\hypertarget{ref-Savary2017}{}}%
Savary, S., Bregaglio, S., Willocquet, L., Gustafson, D., D'Croz, D. M.,
\textbf{Sparks, A.}, \ldots{} Garrett, K. (2017). Crop health and its
global impacts on the components of food security. \emph{Food Security},
\emph{9}(2), 311--327. \url{https://doi.org/10.1007/s12571-017-0659-1}

\leavevmode\vadjust pre{\hypertarget{ref-Sparks2017c}{}}%
\textbf{Sparks, A.} (2017). {getCRUCLdata}: {Use} and explore {CRU CL}
v. 2.0 climatology elements in {R}. \emph{The Journal of Open Source
Software}, \emph{2}(12). \url{https://doi.org/10.21105/joss.00230}

\leavevmode\vadjust pre{\hypertarget{ref-Sparks2017}{}}%
\textbf{Sparks, A.}, Hengl, T., \& Nelson, A. (2017). {GSODR}: {Global}
summary daily weather data in {R}. \emph{The Journal of Open Source
Software}, \emph{2}(10). \url{https://doi.org/10.21105/joss.00177}

\leavevmode\vadjust pre{\hypertarget{ref-Sparks2017a}{}}%
\textbf{Sparks, A.}, Padgham, M., Parsonage, H., \& Pembleton, K.
(2017). {bomrang}: {Fetch Australian} government {Bureau of Meteorology}
weather data. \emph{The Journal of Open Source Software}, \emph{2}(17).
\url{https://doi.org/10.21105/joss.00411}

\leavevmode\vadjust pre{\hypertarget{ref-Duku2016}{}}%
Duku, C., \textbf{Sparks, A.}, \& Zwart, S. J. (2016). Spatial modelling
of rice yield losses in {Tanzania} due to bacterial leaf blight and leaf
blast in a changing climate. \emph{Climatic Change}, \emph{135}(3-4),
569--583. \url{https://doi.org/10.1007/s10584-015-1580-2}

\leavevmode\vadjust pre{\hypertarget{ref-Dossa2015}{}}%
Dossa, G. S., \textbf{Sparks, A.}, Vera Cruz, C., \& Oliva, R. (2015).
Decision tools for bacterial blight resistance gene deployment in
rice-based agricultural ecosystems. \emph{Frontiers in Plant Science},
\emph{6}(305). \url{https://doi.org/10.3389/fpls.2015.00305}

\leavevmode\vadjust pre{\hypertarget{ref-Laborte2015}{}}%
Laborte, A. G., Paguirigan, N. C., Moya, P. F., Nelson, A.,
\textbf{Sparks, A.}, \& Gregorio, G. B. (2015). Farmers' preference for
rice traits: {Insights} from farm surveys in central {Luzon,
Philippines}, 1966-2012. \emph{PLOS ONE}, \emph{10}(8), e0136562.
\url{https://doi.org/10.1371/journal.pone.0136562}

\leavevmode\vadjust pre{\hypertarget{ref-Maloon2015}{}}%
Maloon, J. M., Quilang, E. J. P., Mabalay, M. R. O., Dios, J. L. de,
Jr., A. C. A., Mirandilla, J. R. R., \ldots{} Barbierri, M. (2015).
{Philippine Rice Information System (PRISM)}: Innovating the rice field
data capture and monitoring using smartphone. \emph{Philippine Journal
of Crop Science}.

\leavevmode\vadjust pre{\hypertarget{ref-Sparks2014}{}}%
\textbf{Sparks, A.}, Forbes, G. A., Hijmans, R. J., \& Garrett, K. A.
(2014). Climate change may have limited effect on global risk of potato
late blight. \emph{Global Change Biology}, \emph{20}(12), 3621--3631.
\url{https://doi.org/10.1111/gcb.12587}

\leavevmode\vadjust pre{\hypertarget{ref-Barnwal2013}{}}%
Barnwal, M. K., Kotasthane, A., Magculia, N., Mukherjee, P. K., Savary,
S., Sharma, A. K., \ldots{} Zaidi, N. (2013). A review on crop losses,
epidemiology and disease management of rice brown spot to identify
research priorities and knowledge gaps. \emph{European Journal of Plant
Pathology}, \emph{136}(3), 443--457.
\url{https://doi.org/10.1007/s10658-013-0195-6}

\leavevmode\vadjust pre{\hypertarget{ref-Gaudin2012}{}}%
Gaudin, A. C. M., \textbf{Sparks, A.}, \& Slamet-Loedin, I. H. (2012).
Taking transgenic rice drought screening to the field. \emph{Journal of
Experimental Botany}, \emph{64}(1), 109--117.
\url{https://doi.org/10.1093/jxb/ers313}

\leavevmode\vadjust pre{\hypertarget{ref-Mckinley2012}{}}%
Mckinley, J. D., \textbf{Sparks, A.}, Pede, V. O., \& Duff, B. (2012).
An economic assessment of the impact of mango pulp weevil on the
agricultural sector of {Palawan, Philippines}. \emph{The Philippine
Agricultural Scientist}, \emph{95}(3), 286--292.

\leavevmode\vadjust pre{\hypertarget{ref-Garrett2011}{}}%
Garrett, K. A., Forbes, G. A., Savary, S., Skelsey, P.,
\textbf{Sparks, A.}, Valdivia, C., \ldots{} Yuen, J. (2011). Complexity
in climate-change impacts: An analytical framework for effects mediated
by plant disease. \emph{Plant Pathology}, \emph{60}(1), 15--30.
\url{https://doi.org/10.1111/j.1365-3059.2010.02409.x}

\leavevmode\vadjust pre{\hypertarget{ref-Savary2011}{}}%
Savary, S., Nelson, A., \textbf{Sparks, A.}, Willocquet, L., Duveiller,
E., Mahuku, G., \ldots{} Djurle, A. (2011). International agricultural
research tackling the effects of global and climate changes on plant
diseases in the developing world. \emph{Plant Disease}, \emph{95}(10),
1204--1216. \url{https://doi.org/10.1094/pdis-04-11-0316}
\CSLBlock{doi: 10.1094/PDIS-04-11-0316}

\leavevmode\vadjust pre{\hypertarget{ref-Sparks2011}{}}%
\textbf{Sparks, A.}, Forbes, G. A., Hijmans, R. J., \& Garrett, K. A.
(2011). A metamodeling framework for extending the application domain of
process-based ecological models. \emph{Ecosphere}, \emph{2}(8), art90.
\url{https://doi.org/10.1890/es11-00128.1}

\leavevmode\vadjust pre{\hypertarget{ref-Cheatham2009}{}}%
Cheatham, M. R., Rouse, M. N., Esker, P. D., Ignacio, S., Pradel, W.,
Raymundo, R., \ldots{} Garrett, K. A. (2009). Beyond yield: {Plant}
disease in the context of ecosystem services. \emph{Phytopathology},
\emph{99}(11), 1228--1236.
\url{https://doi.org/10.1094/phyto-99-11-1228}

\leavevmode\vadjust pre{\hypertarget{ref-Esker2008}{}}%
Esker, P. D., \textbf{Sparks, A.}, Campbell, L., Guo, Z., Rouse, M.,
Silwal, S. D., \ldots{} Garrett, K. A. (2008). Ecology and epidemiology
in {R}: Disease forecasting. \emph{The Plant Health Instructor}.
\url{https://doi.org/10.1094/phi-a-2008-0129-01}

\leavevmode\vadjust pre{\hypertarget{ref-Sparks2008a}{}}%
\textbf{Sparks, A.}, Esker, P. D., Antony, G., Campbell, L., Frank, E.
E., Huebel, L., \ldots{} Garrett, K. A. (2008). Ecology and epidemiology
in {R}: Spatial analysis. \emph{The Plant Health Instructor}.
\url{https://doi.org/10.1094/phi-a-2008-0129-03}

\leavevmode\vadjust pre{\hypertarget{ref-Sparks2008}{}}%
\textbf{Sparks, A.}, Esker, P. D., Bates, M., Dall'Acqua, W., Guo, Z.,
Segovia, V., \ldots{} Garrett, K. A. (2008). Ecology and epidemiology in
{R}: Disease progress over time. \emph{The Plant Health Instructor}.
\url{https://doi.org/10.1094/phi-a-2008-0129-02}

\leavevmode\vadjust pre{\hypertarget{ref-Esker2007}{}}%
Esker, P. D., \textbf{Sparks, A.}, Antony, G., Bates, M., Dall'Acqua,
W., Frank, E. E., \ldots{} Garrett, K. A. (2007). Ecology and
epidemiology in {R}: Modeling dispersal gradients. \emph{The Plant
Health Instructor}. \url{https://doi.org/10.1094/PHI-A-2007-1226-03}

\leavevmode\vadjust pre{\hypertarget{ref-Garrett2007}{}}%
Garrett, K. A., Esker, P. D., \& \textbf{Sparks, A.} (2007). An
introduction to the {R} programming environment. \emph{The Plant Health
Instructor}. \url{https://doi.org/10.1094/phi-a-2007-1226-02}

\leavevmode\vadjust pre{\hypertarget{ref-Garrett2007a}{}}%
Garrett, K. A., Esker, P. D., \textbf{Sparks, A.}, \& Scharmann, L. C.
(2007). Writing teaching documents as a class project. \emph{The Plant
Health Instructor}. \url{https://doi.org/10.1094/phi-t-2007-1226-01}

\endgroup

\hypertarget{preprints}{%
\subsection{Preprints}\label{preprints}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs_preprints}{}
\leavevmode\vadjust pre{\hypertarget{ref-Khaliq2020}{}}%
Khaliq, I., Fanning, J., Melloy, P., Galloway, J., Moore, K., Burrell,
D., \& \textbf{Sparks, A.} (2020). The role of conidia in the dispersal
of \emph{{Ascochyta} rabiei}. \emph{bioRxiv}.
\url{https://doi.org/10.1101/2020.05.12.091827}

\endgroup

\hypertarget{book-chapters}{%
\subsection{Book Chapters}\label{book-chapters}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs_books}{}
\leavevmode\vadjust pre{\hypertarget{ref-Kannan2017}{}}%
Kannan, E., Paliwal, A., \& \textbf{Sparks, A.} (2017). Spatial and
temporal patterns of rice production and productivity. In S. Mohanty, P.
G. Chengappa, M. Hedge, J. K. Ladha, S. Baruah, E. Kannan, \& A. V.
Manjunatha (Eds.), \emph{The future rice strategy for india} (First, pp.
39--68). \url{https://doi.org/10.1016/B978-0-12-805374-4.00003-8}

\leavevmode\vadjust pre{\hypertarget{ref-Garrett2016}{}}%
Garrett, K. A., Nita, M., DeWolf, E. D., Esker, P. D., Gomez-Montano,
L., \& \textbf{Sparks, A.} (2016). Plant pathogens as indicators of
climate change. In T. M. Letcher (Ed.), \emph{Climate change: Observed
impacts on earth} (Second, pp. 325--328). Elsevier.

\leavevmode\vadjust pre{\hypertarget{ref-Garrett2014}{}}%
Garrett, K. A., Esker, P. D., \& \textbf{Sparks, A.} (2014). An
introduction to key distributions and models in epidemiology using r. In
K. Stevenson \& M. Jeger (Eds.), \emph{Exercises in plant disease
epidemiology} (2nd ed.). APS Press, Minneapolis, MN.

\leavevmode\vadjust pre{\hypertarget{ref-Garrett2013}{}}%
Garrett, K. A., Forbes, G. A., Gómez, L., Gonzáles, M. A., Gray, M.,
Skelsey, P., \& \textbf{Sparks, A.} (2013). Cambio climático,
enfermedades de las plantas e insectos plaga. In E. Jimenez (Ed.),
\emph{Cambio climático y adaptación en el altiplano boliviano} (Primera
edicion).

\endgroup

\hypertarget{reports}{%
\subsection{Reports}\label{reports}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs_reports}{}
\leavevmode\vadjust pre{\hypertarget{ref-Raitzer2015}{}}%
Raitzer, D. A., \textbf{Sparks, A.}, Huelgas, Z., Maligalig, R.,
Balangue, Z., Launio, C., \ldots{} Ahmed, H. U. (2015). \emph{Is rice
improvement still making a difference? Assessing the economic, poverty
and food security impacts of rice varieties released from 1989 to 2009
in bangladesh, indonesia and the philippines.} {[}A report submitted to
the Standing Panel on Impact Assessment (SPIA), CGIAR Independent
Science and Partnership Council (ISPC). 128 pp.{]}. Retrieved from
Standing Panel on Impact Assessment (SPIA), CGIAR Independent Science;
Partnership Council (ISPC) website:
\url{http://impact.cgiar.org/rice-improvement-still-making-difference}

\leavevmode\vadjust pre{\hypertarget{ref-Geisler2004}{}}%
Geisler, L. J., \& \textbf{Sparks, A.} (2004). \emph{Evaluation of seed
treatment for controlling seedling diseases and compatibility with
rhizobium inoculants, 2003.} (Fungicide and Nematicide Tests No.
59:ST025). The American Phytopathological Society, St. Paul, MN.

\leavevmode\vadjust pre{\hypertarget{ref-Geisler2004a}{}}%
Geisler, L. J., \& \textbf{Sparks, A.} (2004). \emph{Evaluation of seed
treatment fungicides for controlling soybean seedling diseases, 2003}
(Fungicide and Nematicide Tests No. 59:ST025). The American
Phytopathological Society, St. Paul, MN.

\endgroup

\hypertarget{grants}{%
\section{Grants}\label{grants}}

\begin{cventries}
    \cventry{Grains Research and Development Corporation (GRDC)}{Towards effective genetic and sustainable management of Ascochyta blight of chickpea - Ascochyta blight pathogen biology, population dynamics and epidemiology}{AUS}{2020 – 2024}{\begin{cvitems}
\item Led epidemiological and modelling research activities to support Australian grain growers.
\item Funding amount: \$2,552,960 AU
\item Project Lead: Ford, R
\end{cvitems}}
    \cventry{United Nations Food and Agriculture Organisation (FAO): Consultancy}{Country technical consultant}{KHM}{2019 – 2020}{\begin{cvitems}
\item Provided technical expertise and advice to country partners for building an agrometeorology bulletin in three provinces.
\item Funding amount: \$80,000 AU
\end{cvitems}}
    \cventry{Cotton Research and Development Corporation (CRDC): Suppresisve Soils Project}{Ph.D. student scholarship}{Toowoomba, Queensland, AUS}{2019 – 2021}{\begin{cvitems}
\item Funding amount: \$4,657,032 AU
\item Project Lead: Smith, L
\end{cvitems}}
    \cventry{Grains Research and Development Corporation (GRDC): Post-doctoral Fellowship Project USQ1903-003RTX}{A model for predicting chickpea ascochyta blight risk, Parent Project: DAW1810}{AUS}{2019 – 2021}{\begin{cvitems}
\item Supervised post-doctoral research fellow in the development of spatial disease risk model development for chickpea ascochyta blight.
\item Funding amount: \$510,800 AU
\end{cvitems}}
    \cventry{Research and Development Corporation (GRDC)” Research Project DAW1810 Subcontract to USQ from the Government of Western Australia}{Disease epidemiology and management tools for Australian grain growers}{AUS}{2018 – 2021}{\begin{cvitems}
\item Led epidemiological and modelling research activities to support Australian grain growers.
\item Supervised post-doctoral research fellow in the development of spatial disease risk model development for black spot in field pea.
\item Funding amount: \$650,429 AU
\end{cvitems}}
    \cventry{Rural Industries Research and Development Corporation (RIRDC): Project PRJ-010814}{Northern rice Australia - Developing rice growing packages for tropical climates}{Queensland, AUS}{2018 – 2021}{\begin{cvitems}
\item Led research into and developed control methods for common diseases of tropical rice.
\item Co-PIs: Ash, G. and Pembleton, K.
\item Funding amount: \$2 million AU
\end{cvitems}}
    \cventry{Grains Research and Development Corporation (GRDC): Research Project DAQ00186}{One-Year extension to existing project}{AUS}{2017}{\begin{cvitems}
\item Led inter-organisational team in integrated disease management research and disease monitoring activities
\item Funding amount: \$1.2 million AU
\end{cvitems}}
    \cventry{University of Southern Queensland: Research Infrastructure Program 2017}{Laboratory improvements}{Toowoomba, Queensland, AUS}{2017}{\begin{cvitems}
\item Co-PIs: Adorada, D. and Young, A.
\item Funding amount: \$25,000 AU
\end{cvitems}}
    \cventry{Syngenta: Syngenta – IRRI Scientific Knowledge and Exchange Program (SKEP)}{Phase III, Sub-project 1 - Crop health management}{South and Southeast Asia}{2016 – 2019}{\begin{cvitems}
\item Led international and inter-organisational team in integrated disease management research and disease monitoring activities
\item Co-PI: Kee-Fui K. (Syngenta)
\item Funding amount: \$484,274 US
\end{cvitems}}
    \cventry{Bayer: Identifying resistant rice germplasm to false smut using combined screening approaches and understanding the mechanisms underlying rice resistance (Bayer)}{Epidemiology and environmental characterisation of false smut}{PHL}{2015 – 2017}{\begin{cvitems}
\item Led research into development of a predictive model for false smut in rice.
\item Co-PIs: Zhou, B. and Vera Cruz, C. M.
\item Funding amount: \$653,91 US
\end{cvitems}}
    \cventry{Philippine Department of Agriculture: Philippine Rice Information SysteM (PRISM)}{Component B - Crop health monitoring}{PHL}{2013 – 2015}{\begin{cvitems}
\item Led inter-organisational team in integrated disease management research and disease monitoring activities
\item Led efforts to standardise data collection methods and ensure data integrity through the use of mobile devices and cloud-hosted databases.
\item Co-PIs: Nelson, A. (IRRI), Arida, G.S. (PhilRice), Quilang, E. J. P. (PhilRice)
\item Funding amount: \$2.8 million US
\end{cvitems}}
    \cventry{Syngenta – IRRI Scientific Knowledge and Exchange Program (SKEP)}{Phase II, Sub-project 2 - Crop health management}{South and Southeast Asia}{2013 – 2015}{\begin{cvitems}
\item Led international and inter-organisational team in integrated disease management research and disease monitoring activities
\item Co-PI: Kee-Fui K. (Syngenta)
\item Funding amount: \$454,640 US
\end{cvitems}}
\end{cventries}

\hypertarget{awards-and-honours}{%
\section{Awards and Honours}\label{awards-and-honours}}

\begin{cventries}
    \cventry{McCoy, A. G., Noel, Z., Sparks, A., Chilvers M.}{Fourth Most Downloaded MPMI Journal Article of 2019}{Global}{2020}{\begin{cvitems}
\item hagis, an R Package Resource for Pathotype Analysis of Phytophthora sojae Populations Causing Stem and Root Rot of Soybean
\end{cvitems}}
    \cventry{Panczak, R., Baker, P., Gacenga, F., King, R., Li, L., Lodge, J., Lim, C.,  Schnyder, N. and Sparks, A.}{Theo Murphy (Australia) Initiative for support for ‘Re:produce – kick-off meeting of reproducible research network’}{Brisbane, Queensland, AUS}{2019}{\begin{cvitems}
\item Sponsored by The Australian Academy of Science
\end{cvitems}}
    \cventry{Sparks, A.}{Participant in workshop on “Food System Impacts of Pests \& Pathogens in a Changing Climate”}{Aspen, Colorado, USA}{2019}{\begin{cvitems}
\item Aspen Global Change Initiative
\end{cvitems}}
    \cventry{Sparks, A. \& Adorada, D.}{“Best Independent Film” Award for creation of extension articles for extensionAUS website}{Adelaide, South Australia, AUS}{2018}{\begin{cvitems}
\item extensionAUS Field Disease Community of Practice
\end{cvitems}}
    \cventry{Pembleton, K.,  Grundy, G., Sparks, A.}{First Place Award for Paddock to Plate Category, John Conner Hack}{AUS}{2016}{\begin{cvitems}
\item GovHack 2016
\end{cvitems}}
    \cventry{Sparks, A.}{Third Place Graduate Student Oral Presentation and Poster Competition}{Minneapolis, Minnesota, USA}{2008}{\begin{cvitems}
\item 2008 APS North Central Division Meeting
\end{cvitems}}
\end{cventries}

\hypertarget{invited-guest-lectures}{%
\section{Invited Guest Lectures}\label{invited-guest-lectures}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\textbf{Sparks, A.} (2020). \emph{Flashback 2014: Using R at IRRI.}
Invited presentation delivered at ``RUG-PH Seventh Anniversary'' held
via Zoom.

\textbf{Sparks, A.} (2019). \emph{The Impact of Plant Pathology on the
Global Economy.} Invited presentation delivered at the ``IX Symposium on
Updates in Phytopathology'' held in Viçosa, Minas Gerais, BRA.

\textbf{Sparks, A.} (2019). \emph{Delivering and Supporting Open Science
Practices Through Open Plant Pathology.} Invited presentation delivered
at the October 2019 Queensland Chapter APPS Seminar Series, held in
Toowoomba, Queensland, AUS.

\textbf{Sparks, A.} (2019). \emph{Climate Change May Have Limited Effect
on Global Risk of Potato Late Blight.} Invited presentation delivered at
the workshop on ``Food System Impacts of Pests \& Pathogens in a
Changing Climate'' hosted by Aspen Initiative held in Aspen, Colorado,
USA.

\textbf{Sparks, A.} (2019). \emph{Pre and In-Season Tools to Inform
Broadacre Grains Growers} Invited presentation delivered at Southern
Cross University in Lismore, New South Wales, AUS.

\textbf{Sparks, A.} (2019). \emph{From Models to Maps and IDM
In-Between.} Invited presentation delivered at the Australian National
University in Canberra, Australian Capital Territory, AUS.

\textbf{Sparks, A.} (2019). \emph{What's so Open About Plant Pathology?}
Invited presentation delivered at the ``Openness and Reproducibility in
Science'' symposium, hosted by Australian National University, held in
Canberra, Australian Capital Territory, AUS.

\textbf{Sparks, A.} (2018). \emph{University of Southern Queensland,
Centre for Crop Health, Summer Crop Pathology.} Invited presentation
delivered during visit to TEGASC Oak Park Campus in Carlow, IRL.

\textbf{Sparks, A.}, A.D. Nelson, K.A. Garrett, C. Gilligan and K.
Pembleton. (2018). \emph{Upscaling models, downscaling data or the right
model for the right scale of application?} Invited presentation
delivered at the ``2018 International Congress of Plant Pathology'' held
in Boston, Massachusetts, USA.

\textbf{Sparks, A.} (2016). \emph{Using modelling and mapping for
digital insights into diseases in the rice field.} Invited presentation
delivered at the ``2016 Korean Society of Plant Pathology Fall Meeting
and International Conference'' at Seoul National University,
Pyeongchang, Gangwon-do, KOR.

\textbf{Sparks, A.}, N. P. Castilla and G. S. Arida. (2014).
\emph{Taking sustainable crop protection from the field to the cloud.}
Invited presentation delivered at the ``4th International Rice Congress
(IRC2014)'' in Bangkok, THA.

\textbf{Sparks, A.} (2014). \emph{Impact of climate change on rice
diseases.} Invited presentation delivered at the ``Workshop on the
impact of climate change on crop pests and diseases, and adaptation
strategies for the Greater Mekong Sub -- Region (GMS)'' at Hotel
Continental Saigon, Ho Chi Minh City, VNM.

\textbf{Sparks, A.} (2014). \emph{Epidemiology and Disease Management of
rice brown spot: Research priorities and knowledge gaps.} Invited
presentation delivered at the ``66th Annual Indian Phytopathological
Society Meeting'' at Indira Gandhi Krishi Vishwavidyalaya University,
Raipur, IND.

\textbf{Sparks, A.} (2013). \emph{Biosecurity risks in Southeast Asia
impacting on human food supplies.} Invited presentation delivered at the
``Pacific Environmental Security Forum'' hosted by the Australian
Department of Defence (ADoD) and U. S. Pacific Command (USPACOM) in
Sydney, New South Wales, AUS.

\textbf{Sparks, A.} (2010). \emph{Global potato late blight risk in
response to climate change, possible futures for a historic disease.}
Invited presentation presented at ``Emerging infectious diseases in
response to climate change'' hosted by New York Academy of Sciences in
New York, New York, USA.

\endgroup

\hypertarget{papers-and-posters-presented}{%
\section{Papers and Posters
Presented}\label{papers-and-posters-presented}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs_proceedings}{}
\leavevmode\vadjust pre{\hypertarget{ref-Adorada2019}{}}%
Adorada, D. L., Adorada, E. E., Gonzales, P., \& \textbf{Sparks, A.}
(2019). Pathogenicity and aggressiveness of \emph{macrophomina
phaseolina} isolates to sorghum in {Australia's} northern grains region.
\emph{Proceedings of the 2019 Australian Summer Grains Conference}.

\leavevmode\vadjust pre{\hypertarget{ref-Sparks2019ASGC}{}}%
\textbf{Sparks, A.}, Diggle, A., Galloway, J., Kelly, L., Melloy, P., \&
Weir, D. (2019). A new tool to support mungbean growers and advisers in
the fight against powdery mildew. \emph{Proceedings of the 2019
Australian Summer Grains Conference}.

\leavevmode\vadjust pre{\hypertarget{ref-Vaghefi2019}{}}%
Vaghefi, N., Adorada, D. L., Adorada, E. E., Kelly, L., Young, A., \&
\textbf{Sparks, A.} (2019). Characterising the genotypic diversity of
{\emph{Curtobacterium flaccumfaciens}} pv. \emph{Flaccumfaciens}, the
cause of tan spot on mungbean. \emph{Proceedings of the 2019 Australian
Summer Grains Conference}.

\leavevmode\vadjust pre{\hypertarget{ref-Adorada2018}{}}%
Adorada, D. L., Gonzales, P., McKay, A., Vaghefi, N., \&
\textbf{Sparks, A.} (2018). A broad look at charcoal rot in the
{Northern Region} broadacre crops through soil sampling and in-crop
surveys. \emph{Proceedings of the 10\textsuperscript{th} australasian
soilborne diseases symposium}. Presented at the National Wine Centre.

\leavevmode\vadjust pre{\hypertarget{ref-Adorada2017}{}}%
Adorada, D. L., Thompson, S. M., Grams, R. A., Adorada, E. E.,
\textbf{Sparks, A.}, Wright, G., \ldots{} Ash, G. J. (2017). Fungi and
bacteria associated with the {Peanut Kernel Shrivel (PKS)} disease in
the {Bundaberg} region. \emph{Proceedings of the australasian plant
pathology society 2017 meeting}.

\leavevmode\vadjust pre{\hypertarget{ref-Cucak2017}{}}%
Cucak, M., \textbf{Sparks, A.}, Fealy, R., Griffin, D., Lambkin, K., \&
Kildea, S. (2017). Lowering thresholds of qualitative plant risk
prediction algorithms: Sensitivity versus specificity of {Irish Rules}
for potato late blight development. \emph{Euroblight Workshop}.

\leavevmode\vadjust pre{\hypertarget{ref-Kelly2017}{}}%
Kelly, L., White, J., Sharman, M., Brier, H., Williams, L., Grams, R.,
\ldots{} \textbf{Sparks, A.} (2017). Mungbean and sorghum disease
update. \emph{GRDC Updates (Jondaryan)}. Presented at the Jondaryan
Woolshed. GRDC.

\leavevmode\vadjust pre{\hypertarget{ref-Sparks2017b}{}}%
\textbf{Sparks, A.}, Castilla, N. P., \& Sander, B. O. (2017). Do
alternate wetting and drying irrigation technologies and nitrogen rates
affect rice sheath blight? \emph{Proceedings of the {Australasian Plant
Pathology Society} 2017 meeting}.

\leavevmode\vadjust pre{\hypertarget{ref-Jaisong2015}{}}%
Jaisong, S., Castilla, N. P., Magculia, C. T., Savary, S., Pangga, I.
B., \& \textbf{Sparks, A.} (2015). Evaluation of correlation methods for
co-occurrence network construction of rice crop health survey data.
\emph{Proceedings of the Australasian Plant Pathology Society 2015
Meeting}.

\leavevmode\vadjust pre{\hypertarget{ref-Sparks2015}{}}%
\textbf{Sparks, A.}, \& Noel, M. (2015). Mapping rice diseases for
targeted deployment of resistant varieties in {India}. \emph{Proceedings
of the australasian plant pathology society 2015 meeting}.

\leavevmode\vadjust pre{\hypertarget{ref-Sparks2013}{}}%
\textbf{Sparks, A.}, Anaurio, J., Duku, C., Noel, M., \& Raitzer, D.
(2013). Modeling the impact of disease resistance on rice yields in the
{Philippines} and {Indonesia}. \emph{Proceedings of the {Australasian
Plant Pathology Society} 2013 meeting}. Technical report. CGIAR - SPIA.

\leavevmode\vadjust pre{\hypertarget{ref-Sparks2013a}{}}%
\textbf{Sparks, A.}, Duku, C., Noel, M., \& Zwart, S. J. (2013). Spatial
modelling of rice yield losses due to bacterial leaf blight and leaf
blast in a changing climate. \emph{{Acta Phytopathologica Sinica}},
\emph{43}.

\leavevmode\vadjust pre{\hypertarget{ref-Magculia2012}{}}%
Magculia, N. J., \& \textbf{Sparks, A.} (2012). Predisposition factors
affecting brown spot disease development in rice. \emph{Phytopathology},
\emph{102:S4.74}.

\leavevmode\vadjust pre{\hypertarget{ref-Savary2012}{}}%
Savary, S., \textbf{Sparks, A.}, Nelson, A., McRoberts, N., \& Esker, P.
D. (2012). Putting information to use: {Decisions} at different scales.
\emph{Phytopathology}, \emph{102:S4.162}.

\leavevmode\vadjust pre{\hypertarget{ref-Sparks2012}{}}%
\textbf{Sparks, A.}, Savary, S., \& Nelson, A. (2012). Preventing what
ails rice with a strategic, statistical, prescriptive model system.
\emph{Phytopathology}, \emph{102:S4.113}.

\leavevmode\vadjust pre{\hypertarget{ref-Ballesefin2011}{}}%
Ballesefin, G. B., Pede, V. O., \& \textbf{Sparks, A.} (2011). Income
inequality and economic growth in the {Philippines}. \emph{The
conference secretariat, 2011 {PAEDA} biennial convention}.

\leavevmode\vadjust pre{\hypertarget{ref-McKinley2011}{}}%
McKinley, J., Pede, V. O., \textbf{Sparks, A.}, \& Duff, B. (2011). An
economic assessment of the impact of mango pulp weevil on the
agricultural sector of {Palawan, Philippines}. \emph{The conference
secretariat, 2011 {PAEDA} biennial convention}.

\leavevmode\vadjust pre{\hypertarget{ref-Sparks2011a}{}}%
\textbf{Sparks, A.}, Shah, D., DeWolf, E., Madden, L., Paul, P., \&
Willyerd, K. (2011). Refined empirical models for predicting {Fusarium}
head blight epidemics in the {United States}. \emph{Phytopathology},
\emph{101:S223}.

\leavevmode\vadjust pre{\hypertarget{ref-Willocquet2011}{}}%
Willocquet, L., Nelson, A., \textbf{Sparks, A.}, Laborte, A., \& Savary,
S. (2011). Crop losses in highly populated areas: {A} global
perspective. \emph{Phytopathology}, \emph{101:S223}.

\leavevmode\vadjust pre{\hypertarget{ref-Sparks2010}{}}%
\textbf{Sparks, A.}, Forbes, G., Hijmans, R., \& Garrett, K. (2010).
Metamodels for scaling potato late blight risk analysis in climate
change scenarios. \emph{Phytopathology}, \emph{100:S121}.

\leavevmode\vadjust pre{\hypertarget{ref-Garrett2009}{}}%
Garrett, K., Forbes, G., Pande, S., Savary, S., \textbf{Sparks, A.},
Valdivia, C., \ldots{} Willocquet, L. (2009). Anticipating and
responding to biological complexity in the effects of climate change on
agriculture. \emph{IOP conference series: Earth and environmental
science}, \emph{6}. \url{https://doi.org/10.1088/1755-1307/6/7/372007}

\leavevmode\vadjust pre{\hypertarget{ref-Sparks2009}{}}%
\textbf{Sparks, A.}, Forbes, G., \& Garrett, K. A. (2009). Adapting
disease forecasting models to coarser scales: {Global} potato late
blight prediction. \emph{Phytopathology}, \emph{99:S122}.

\leavevmode\vadjust pre{\hypertarget{ref-Sparks2008b}{}}%
\textbf{Sparks, A.}, Raymundo, R., Simon, R., Forbes, G., \& Garrett, K.
A. (2008). Regional predictions of potato late blight risk in a {GIS}
incorporating disease resistance profiles, climate change, and risk
neighborhoods. \emph{Phytopathology}, \emph{98:S149}.

\endgroup

\hypertarget{campus-or-departmental-talks}{%
\section{Campus or Departmental
Talks}\label{campus-or-departmental-talks}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\textbf{Sparks, A.} (2019). \emph{Improving management options,
epidemiology knowledge and tools to manage crop diseases.} for Curtin
University Centre for Crop Disease Management visit to University of
Southern Queensland Centre for Crop Health in Toowoomba, Queensland,
AUS.

\textbf{Sparks, A.} (2019). \emph{Completing the Picture. Integrating
Plant Disease Into Ag Systems Modelling} for University of Southern
Queensland Agriculture Systems Precinct grand opening held in Toowoomba,
Queensland, AUS.

\textbf{Sparks, A.} (2016). \emph{How to Combine Models and Maps When
All Models Are Wrong and Maps Lie} for University of Southern Queensland
Centre for Crop Health Seminar Series at University of Southern
Queensland, Toowoomba, Queensland, AUS.

\textbf{Sparks, A.} (2016). \emph{USQ CCH Modelling.} at University of
Southern Queensland in Toowoomba, Queensland, AUS

\textbf{Sparks, A.} (2015). \emph{I've a feeling we're not in Kansas
anymore.} Introductory seminar for University of Southern Queensland in
Toowoomba, Queensland, AUS.

\textbf{Sparks, A.} (2015). \emph{Working across scales: Integrating
satellite mapping and field studies for policy, crop management and
forecasting.} for Bill Gates visit to IRRI at IRRI in Los Baños, Laguna,
PHL.

\textbf{Sparks, A.} (2014). \emph{Looking forward, a workplan for
integrated disease management at IRRI.} Work Vision Seminar at IRRI in
Los Baños, Laguna, PHL.

\textbf{Sparks, A.} (2013). \emph{Don't get caught with your plants
down. Consult a plant pathologist.} Invited presentation for IRRI
Thursday Seminar Series in Los Baños, Laguna, PHL.

\textbf{Sparks, A.} (2013). \emph{Current status of rice pathogens over
geographic regions.} Presented for Taiwan Delegation visiting IRRI in
Los Baños, Laguna, PHL.

\textbf{Sparks, A.} (2011). \emph{Crop Modelling at IRRI.} at IRRI in
Los Baños, Laguna, PHL.

\textbf{Sparks, A.} (2011). \emph{Mapping the future.} IRRI Plant
Breeding Genetics and Biotechnology division Seminar Series in Los
Baños, Laguna, PHL.

\endgroup

\hypertarget{extension-and-community-outreach}{%
\section{Extension and Community
Outreach}\label{extension-and-community-outreach}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs_extension}{}
\leavevmode\vadjust pre{\hypertarget{ref-Eyre2020}{}}%
Eyre, J., \textbf{Sparks, A.}, Miles, M., \& Rodriguez, D. (2020).
Consider soil water storage before sowing a grain sorghum crop.
\emph{GRDC Ground Cover}. Retrieved from
\url{https://groundcover.grdc.com.au/story/6591350/is-late-sowing-of-sorghum-a-viable-option-in-the-northern-region/}

\leavevmode\vadjust pre{\hypertarget{ref-Sparks2020}{}}%
\textbf{Sparks, A.}, Melloy, P., Diggle, A., \& Galloway, J. (2020).
Make better fungicide application decisions for mungbean powdery mildew
with the new {PowderyMildewMBM} app. \emph{{GRDC} Update Papers}.
Retrieved from
\url{https://grdc.com.au/resources-and-publications/grdc-update-papers/tab-content/grdc-update-papers/2020/07/make-better-fungicide-application-decisions-for-mungbean-powdery-mildew-with-the-new-powderymildewmbm-app}

\leavevmode\vadjust pre{\hypertarget{ref-Adorada2019a}{}}%
Adorada, D., \& \textbf{Sparks, A.} (2019). Low levels of disease
persist during the drier summer season in parts of the northern region.
\emph{GRDC Communities}. Retrieved from
\url{https://communities.grdc.com.au/field-crop-diseases/low-disease-drier-summer-northern/}

\leavevmode\vadjust pre{\hypertarget{ref-Adorada2019b}{}}%
Adorada, D., \& \textbf{Sparks, A.} (2019). Moisture saves sorghum from
disease in parts of the northern region. \emph{GRDC Communities}.
Retrieved from
\url{https://communities.grdc.com.au/field-crop-diseases/sorghum-disease-survey/}

\leavevmode\vadjust pre{\hypertarget{ref-Adorada2019c}{}}%
Adorada, D., Vaghefi, N., \& \textbf{Sparks, A.} (2019). Re-visiting
management options for charcoal rot in sorghum. \emph{GRDC Communities}.
Retrieved from
\url{https://communities.grdc.com.au/field-crop-diseases/re-visiting-management-options-charcoal-rot-sorghum/}

\leavevmode\vadjust pre{\hypertarget{ref-Sparks2019a}{}}%
\textbf{Sparks, A.} (2019). Where and when does charcoal rot in sorghum
occur? \emph{GRDC Communities}. Retrieved from
\url{https://communities.grdc.com.au/field-crop-diseases/charcoal-rot-sorghum/}

\leavevmode\vadjust pre{\hypertarget{ref-Sparks2019b}{}}%
\textbf{Sparks, A.}, \& Purushotham, N. (2019). Last season's summer
grain diseases \& sorghum charcoal rot. \emph{GRDC Communities Podcast}.
Retrieved from
\url{https://communities.grdc.com.au/field-crop-diseases/summer-crop-diseases-podcast/}

\leavevmode\vadjust pre{\hypertarget{ref-Adorada2019d}{}}%
Adorada, D., Kelly, L., Vaghefi, N., \& \textbf{Sparks, A.} (2018).
Summer paddock survey finds fungal and bacterial diseases decreased but
not eliminated. \emph{GRDC Communties}. Retrieved from
\url{https://communities.grdc.com.au/field-crop-diseases/summer-paddock-survey/}

\leavevmode\vadjust pre{\hypertarget{ref-McKay2018}{}}%
McKay, A., Simpfendorfer, S., Gupta, V., Bithell, S., Moore, K., Daniel,
R., \ldots{} Holloway, G. (2018). {PREDICTA{\textregistered} B} update
and new tests for 2018. \emph{GRDC Update Papers}. Retrieved from
\url{https://grdc.com.au/resources-and-publications/grdc-update-papers/tab-content/grdc-update-papers/2018/03/predictab-update-and-new-tests-for-2018}

\leavevmode\vadjust pre{\hypertarget{ref-Adorada2017}{}}%
Adorada, D., Sigel, L., Kelly, L., \& \textbf{Sparks, A.} (2017).
Diagnosing plant diseases: {What} do we ask and why do we ask for it?
\emph{GRDC Communities}. Retrieved from
\url{https://communities.grdc.com.au/field-crop-diseases/diagnosing-plant-diseases-ask-ask/}

\leavevmode\vadjust pre{\hypertarget{ref-Kelly2017}{}}%
Kelly, L., White, J., Sharman, M., Brier, H., Williams, L., Grams, R.,
\ldots{} \textbf{Sparks, A.} (2017). Mungbean and sorghum disease
update. \emph{19th July 2017 Grains Research Update: Jondaryan}, 11--22.
Retrieved from
\url{https://grdc.com.au/resources-and-publications/grdc-update-papers/tab-content/grdc-update-papers/2017/07/mungbean-and-sorghum-disease-update}

\leavevmode\vadjust pre{\hypertarget{ref-Sparks2017}{}}%
\textbf{Sparks, A.}, \& Kelly, L. (2017). Mungbean powdery mildew
management with fungicide. \emph{GRDC Communities}. Retrieved from
\url{https://communities.grdc.com.au/field-crop-diseases/mungbean-powdery-mildew-fungicide/}

\leavevmode\vadjust pre{\hypertarget{ref-Choi2014b}{}}%
Choi, I. R., \textbf{Sparks, A.}, Castilla, N. P., \& Vera Cruz, C. M.
(2014). Rice stripe virus disease. \emph{{IRRI} Rice Knowledge Bank}.
Retrieved from
\url{http://www.knowledgebank.irri.org/decision-tools/rice-doctor/rice-doctor-fact-sheets/item/rice-stripe}

\leavevmode\vadjust pre{\hypertarget{ref-Choi2014}{}}%
Choi, I. R., \textbf{Sparks, A.}, \& Vera Cruz, C. M. (2014). Red
stripe. \emph{{IRRI} Rice Knowledge Bank}. Retrieved from
\url{http://www.knowledgebank.irri.org/training/fact-sheets/pest-management/diseases/item/narrow-brown-spot}

\leavevmode\vadjust pre{\hypertarget{ref-Sparks2014f}{}}%
\textbf{Sparks, A.}, Castilla, N. P., \& Savary, S. (2014). Narrow brown
spot. \emph{{IRRI} Rice Knowledge Bank}. Retrieved from
\url{http://www.knowledgebank.irri.org/training/fact-sheets/pest-management/diseases/item/narrow-brown-spot}

\leavevmode\vadjust pre{\hypertarget{ref-Sparks2014}{}}%
\textbf{Sparks, A.}, Castilla, N. P., \& Vera Cruz, C. M. (2014).
Bakanae. \emph{{IRRI} Rice Knowledge Bank}. Retrieved from
\url{http://www.knowledgebank.irri.org/training/fact-sheets/pest-management/diseases/item/bakanae}

\leavevmode\vadjust pre{\hypertarget{ref-Sparks2014b}{}}%
\textbf{Sparks, A.}, Castilla, N. P., \& Vera Cruz, C. M. (2014). Blast
(leaf and collar). \emph{{IRRI} Rice Knowledge Bank}. Retrieved from
\url{http://www.knowledgebank.irri.org/training/fact-sheets/pest-management/diseases/item/blast-leaf-collar}

\leavevmode\vadjust pre{\hypertarget{ref-Sparks2014c}{}}%
\textbf{Sparks, A.}, Castilla, N. P., \& Vera Cruz, C. M. (2014). Blast
(node and neck). \emph{{IRRI} Rice Knowledge Bank}. Retrieved from
\url{http://www.knowledgebank.irri.org/training/fact-sheets/pest-management/diseases/item/blast-node-neck}

\leavevmode\vadjust pre{\hypertarget{ref-Sparks2014a}{}}%
\textbf{Sparks, A.}, Castilla, N. P., \& Vera Cruz, C. M. (2014). Brown
spot. \emph{{IRRI} Rice Knowledge Bank}. Retrieved from
\url{http://www.knowledgebank.irri.org/training/fact-sheets/pest-management/diseases/item/brown-spot}

\leavevmode\vadjust pre{\hypertarget{ref-Sparks2014e}{}}%
\textbf{Sparks, A.}, Castilla, N. P., \& Vera Cruz, C. M. (2014). Leaf
scald. \emph{{IRRI} Rice Knowledge Bank}. Retrieved from
\url{http://www.knowledgebank.irri.org/training/fact-sheets/pest-management/diseases/item/leaf-scald}

\leavevmode\vadjust pre{\hypertarget{ref-Sparks2014g}{}}%
\textbf{Sparks, A.}, Castilla, N. P., \& Vera Cruz, C. M. (2014). Sheath
rot. \emph{{IRRI} Rice Knowledge Bank}. Retrieved from
\url{http://www.knowledgebank.irri.org/training/fact-sheets/pest-management/diseases/item/sheath-rot}

\leavevmode\vadjust pre{\hypertarget{ref-Sparks2014d}{}}%
\textbf{Sparks, A.}, Castilla, N. P., \& Vera Cruz, C. M. (2014).
Tungro. \emph{{IRRI} Rice Knowledge Bank}. Retrieved from
\url{http://www.knowledgebank.irri.org/training/fact-sheets/pest-management/diseases/item/sheath-blight}

\leavevmode\vadjust pre{\hypertarget{ref-Sparks2014h}{}}%
\textbf{Sparks, A.}, Castilla, N. P., Vera Cruz, C. M., \& Elazegui, F.
A. (2014). Stem rot. \emph{{IRRI} Rice Knowledge Bank}. Retrieved from
\url{http://www.knowledgebank.irri.org/training/fact-sheets/pest-management/diseases/item/stem-rot}

\leavevmode\vadjust pre{\hypertarget{ref-Sparks2014i}{}}%
\textbf{Sparks, A.}, Choi, I. R., \& Castilla, N. (2014). Rice yellow
mottle virus. \emph{{IRRI} Rice Knowledge Bank}. Retrieved from
\url{http://www.knowledgebank.irri.org/training/fact-sheets/pest-management/diseases/item/rice-yellow-mottle-virus-fact-sheet}

\leavevmode\vadjust pre{\hypertarget{ref-Sparks2008a}{}}%
\textbf{Sparks, A.}, \& Kennelly, M. (2008). Bacterial ring rot of
potato. \emph{Kansas State University}. Retrieved from
\url{https://krex.k-state.edu/dspace/handle/2097/21720}

\leavevmode\vadjust pre{\hypertarget{ref-Sparks2008b}{}}%
\textbf{Sparks, A.}, \& Kennelly, M. (2008). Blackleg of potato.
\emph{Kansas State University}. Retrieved from
\url{https://krex.k-state.edu/dspace/handle/2097/21719}

\leavevmode\vadjust pre{\hypertarget{ref-Sparks2002b}{}}%
\textbf{Sparks, A.} (2002). Fusarium root rot. \emph{Nebraska Crop
Watch}. Retrieved from
\url{https://cropwatch.unl.edu/plantdisease/corn/fusarium-root-rot}

\leavevmode\vadjust pre{\hypertarget{ref-Sparks2002a}{}}%
\textbf{Sparks, A.} (2002). Fusarium stalk rot. \emph{Nebraska Crop
Watch}. Retrieved from
\url{https://cropwatch.unl.edu/plantdisease/corn/fusarium-stalk-rot}

\endgroup

\hypertarget{teaching-experience}{%
\section{Teaching Experience}\label{teaching-experience}}

\hypertarget{classroom}{%
\subsection{Classroom}\label{classroom}}

\begin{cventries}
    \cventry{Teaching Assistant}{Kansas State University}{Manhattan, Kansas, USA}{2006}{\begin{cvitems}
\item Epidemiology and Ecology of Plant Pathogens
\end{cvitems}}
    \cventry{Teaching Assistant}{Kansas State University}{Manhattan, Kansas, USA}{2008}{\begin{cvitems}
\item Introduction to Plant Pathology Laboratory Section
\end{cvitems}}
\end{cventries}

\hypertarget{workshops}{%
\subsection{Workshops}\label{workshops}}

\begin{cventries}
    \cventry{Software Carpentries R for Reproducible Scientific Analysis}{QCIF (Queensland Cyber Infrastructure Foundation)}{Zoom}{Aug. 2020}{\begin{cvitems}
\item Lead Instructor
\end{cvitems}}
    \cventry{Software Carpentries R for Reproducible Scientific Analysis}{QCIF (Queensland Cyber Infrastructure Foundation)}{Zoom}{Jun. 2020}{\begin{cvitems}
\item Lead Instructor
\end{cvitems}}
    \cventry{Data Carpentries Data Organization in Spreadsheets for Ecologists}{FAO and Cambodia GDA}{Phnom Penh, KHM}{Dec. 2019}{\begin{cvitems}
\item Organiser and Lead Instructor
\end{cvitems}}
    \cventry{R Markdown for Scientists}{Australasian Plant Pathology Society}{Melbourne, Victoria, AUS}{Nov. 2019}{\begin{cvitems}
\item Organiser and Lead Instructor
\end{cvitems}}
    \cventry{R for Scientific Analysis}{Southern Cross University}{Lismore, New South Wales, AUS}{Jul. 2019}{\begin{cvitems}
\item Lead Instructor
\end{cvitems}}
    \cventry{Software Carpentries Python Workshop}{University of Southern Queensland}{Springfield, Queensland, AUS}{Oct. 2019}{\begin{cvitems}
\item Helper
\end{cvitems}}
    \cventry{Software Carpentries R for Reproducible Scientific Analysis}{University of Southern Queensland}{Toowoomba, Queensland, AUS}{Jun. 2019}{\begin{cvitems}
\item Co-organiser and Instructor
\end{cvitems}}
    \cventry{Software Carpentries Python Workshop}{University of Southern Queensland}{Springfield, Queensland, AUS}{Oct. 2018}{\begin{cvitems}
\item Helper
\end{cvitems}}
    \cventry{Software Carpentries R for Reproducible Scientific Analysis}{University of Southern Queensland}{Toowoomba, Queensland, AUS}{Jun. 2018}{\begin{cvitems}
\item Co-organiser and Instructor
\end{cvitems}}
    \cventry{Software Carpentries R for Reproducible Scientific Analysis}{University of Southern Queensland}{Toowoomba, Queensland, AUS}{Jun. 2017}{\begin{cvitems}
\item Helper
\end{cvitems}}
    \cventry{Workshop on Integrated Rice Disease Management and Training on Statistical Analysis}{Bureau of Rice Research and Development, Rice Department, Bangkok}{Chiang Mai, THL}{Jun. 2012}{\begin{cvitems}
\item Co-organiser and Instructor
\end{cvitems}}
\end{cventries}

\hypertarget{service}{%
\section{Service}\label{service}}

\begin{cventries}
    \cventry{Reproducibility Editor}{Tropical Plant Pathology}{Global}{2020 – Present}{}\vspace{-4.0mm}
    \cventry{R Programming Helper}{University of Southern Queensland Hacky Hour}{Toowoomba, Queensland, AUS}{2019 – Present}{}\vspace{-4.0mm}
    \cventry{Guest Editor for Special Issue on Remote Sensing and Crop Health}{MDPI Remote Sensing}{Global}{2019 – Present}{}\vspace{-4.0mm}
    \cventry{Mentor}{R4ds (https://rfordatascience.slack.com)}{Global}{2019 – Present}{}\vspace{-4.0mm}
    \cventry{Co-Founder and Co-Director}{Open Plant Pathology (https://openplantpathology.org)}{Global}{2018 – Present}{}\vspace{-4.0mm}
    \cventry{Member}{University of Southern Queensland Athena SWAN (Scientific Women’s Academic Network) SAGE (Science in Australia Gender Equality) Submission Committee}{Toowoomba, Queensland, AUS}{2018 – Present}{}\vspace{-4.0mm}
    \cventry{Member}{International Congress of Plant Pathology (ICPP) Crop Loss Committee}{Global}{2018 – Present}{}\vspace{-4.0mm}
    \cventry{Epidemiology Section Editor}{Tropical Plant Pathology}{Global}{2017 – Present}{}\vspace{-4.0mm}
    \cventry{Member}{University of Southern Queensland Centre for Crop Health Advisory Committee}{Toowoomba, Queensland, AUS}{2016 – Present}{}\vspace{-4.0mm}
    \cventry{Member}{Australia National Plant Biosecurity Diagnostic Network}{AUS}{2016 – Present}{}\vspace{-4.0mm}
    \cventry{Member}{GRDC Communities of Practice: Field Crop Diseases}{AUS}{2018 – 2019}{}\vspace{-4.0mm}
    \cventry{Member}{extensionAUS: Field Crops Diseases Community of Practice}{AUS}{2016 – 2018}{}\vspace{-4.0mm}
    \cventry{Member}{International Congress of Plant Pathology (ICPP) Epidemiology Committee}{Global}{2013 – Present}{}\vspace{-4.0mm}
    \cventry{Coordinator}{IRRI Crop and Environmental Sciences Division Seminar Series}{Los Baños, Laguna, PHL}{2013 – 2015}{}\vspace{-4.0mm}
    \cventry{Member}{IRRI One Corporate System (OCS) Advisory Committee}{Los Baños, Laguna, PHL}{2013 – 2015}{}\vspace{-4.0mm}
    \cventry{Member}{IRRI National Employee Recognition Program Committee}{Los Baños, Laguna, PHL}{2013 – 2015}{}\vspace{-4.0mm}
    \cventry{President}{K-State Plant Pathology Graduate Student Club}{Manhattan, Kansas, USA}{2006 – 2007}{}\vspace{-4.0mm}
    \cventry{Member}{K-State Plant Pathology Webpage Advisory Committee}{Manhattan, Kansas, USA}{2005 – 2007}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{certifications}{%
\section{Certifications}\label{certifications}}

\begin{cventries}
    \cventry{Certified Instructor}{Carpentries}{Global}{2019 - Present}{}\vspace{-4.0mm}
    \cventry{Candidate number: P2R/009385}{PRINCE2 Foundation, HiLogic Pty Ltd.}{Global}{2014 – Present}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{memberships}{%
\section{Memberships}\label{memberships}}

\begin{cventries}
    \cventry{Member}{USQ Ally Network}{Toowoomba, Queensland, AUS}{2019 – Present}{}\vspace{-4.0mm}
    \cventry{Member}{Australia New Zealand Open Research Network (ANZORN)}{AUS and NZL}{2019 – Present}{}\vspace{-4.0mm}
    \cventry{Member}{rOpenSci}{Global}{2017 – Present}{}\vspace{-4.0mm}
    \cventry{Member}{Australasian Plant Pathology Society}{AUS and NZL}{2013 – Present}{}\vspace{-4.0mm}
    \cventry{Founding Member}{Philippines R Users Group (RUG-PH)}{Manila, PHL}{2013 – Present}{}\vspace{-4.0mm}
\end{cventries}

\end{document}
