---
#citeproc: yes
graphics: yes
name: Adam H.
surname: Sparks
headcolor: 414141
#qualifications: 
position: "Associate Professor"
address: "University of Southern Queensland, Centre for Crop Health, West St., Toowoomba, Queensland 4350 AUS"
phone: "+61 (4) 15489422"
www: adamhsparks.com
email: "adam@adamhsparks.com"
twitter: adamhsparks
github: adamhsparks
#linkedin: adamhsparks
orcid: 0000-0002-0061-8359
aboutme: |
  I have demonstrated consistent success both in non-profit international NGO and academic settings and have an extensive background of experiences in working with diverse partners.
date: '`r format(Sys.Date(), "%B %d, %Y")`'
csl: "csl/apa6-cv.csl"
nocite: "@*"
knit: bookdown::render_book
bibliography_articles: "bib/articles.bib"
bibliography_books: "bib/books.bib"
bibliography_proceedings: "bib/proceedings.bib"
bibliography_reports: "bib/reports.bib"
bibliography_Rpackages: "bib/Rpackages.bib"
---

```{r setup, include=FALSE, cache = FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(RefManageR)
RefManageR::BibOptions(check.entries = FALSE,
           bib.style = "authoryear",
           sorting = "ynt",
           cite.style = "year",
           style = "markdown",
           hyperlink = TRUE,
           dashed = FALSE)

library(vitae)
library(tidyverse)
library(ezpickr)
```

# Employment History

```{r employment}
ezpickr::pick("data/working-experience.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Education and Qualifications

```{r education}
ezpickr::pick("data/education.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Publications

## Selected Publications

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_articles}
:::
\endgroup

## Book Chapters

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_books}
:::
\endgroup

## Reports

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_reports}
:::
\endgroup

# Presentations and Posters in Proceedings

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_proceedings}
:::
\endgroup

# R&nbsp;Packages

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_Rpackages}
:::
\endgroup

# Funding Attracted

```{r grant}
ezpickr::pick("data/grant.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(with, when, what, where, why)
```

# Mentoring

```{r mentorship}
ezpickr::pick("data/mentorship.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(with, when, what, where, why)
```

# Awards and Honours

```{r award}
ezpickr::pick("data/award.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Invited Guest Lectures

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

`r knitr::knit_child("data/invited.txt")`

\endgroup

# Service

```{r service, eval = TRUE}
ezpickr::pick("data/service.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Certifications

```{r certifications, eval = TRUE}
ezpickr::pick("data/certification.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Memberships

```{r memberships, eval = TRUE}
ezpickr::pick("data/membership.xlsx") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Skills

## Programming Abilities

  * Programming: R (author and maintain packages on CRAN)
  * Operating System: Unix/Linux (install and maintain Linux)
  * Others: Git, Docker, Travis CI, LaTeX, Markdown and RMarkdown

## Software

  * Statistical Software: R
  * Office Software Packages: Microsoft Office, LibreOffice and Google Suites
  * GIS Software: R, QGIS, ArcGIS

<!-- *`r Sys.Date()`* -->
