---
graphics: yes
name: Adam H.
surname: Sparks
headcolor: 414141
#qualifications: 
position: "Senior Research Scientist, Bioeconomic Modeller"
address: "State of Western Australia, Department of Primary Industries and Regional Development, Level 5, 1 Nash St., Perth WA, 6000"
phone: "+61 (4) 15489422"
www: adamhsparks.com
email: "adam.sparks@dpird.wa.gov.au"
twitter: adamhsparks
github: adamhsparks
#linkedin: adamhsparks
orcid: 0000-0002-0061-8359
aboutme: |
  I have demonstrated consistent success both in non-profit international NGO and academic settings and have an extensive background of experiences in working with diverse partners.
date: '`r format(Sys.Date(), "%B %d, %Y")`'
csl: "csl/apa6-cv.csl"
nocite: "@*"
knit: bookdown::render_book
bibliography_articles: "bib/articles.bib"
bibliography_books: "bib/books.bib"
bibliography_extension: "bib/extension_pubs.bib"
bibliography_proceedings: "bib/proceedings.bib"
bibliography_reports: "bib/reports.bib"
bibliography_preprints: "bib/preprints.bib"
---

```{r setup, include=FALSE, cache = FALSE}
library(magrittr)
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)

library(RefManageR)
RefManageR::BibOptions(
  check.entries = FALSE,
  bib.style = "authoryear",
  sorting = "ynt",
  cite.style = "year",
  style = "markdown",
  hyperlink = TRUE,
  dashed = FALSE
)
```

# Professional Experience

```{r professional-employment}
x <- readr::read_csv("data/professional-employment.csv")
y <- readr::read_csv("data/research-experience.csv")

dplyr::bind_rows(x, y) %>% 
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Education and Qualifications

```{r education}
readr::read_csv("data/education.csv") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Related Professional Skills

## Programming Abilities

  * Programming: R (author and maintain packages on CRAN)
  * Operating System: macOS, Unix/Linux (install and maintain Linux)
  * Others: Git, Docker, LaTeX, Markdown and RMarkdown

## Software

  * Statistical Software: R
  * Office Software Packages: Microsoft Office/365, LibreOffice and Google Suites
  * GIS Software: R, QGIS, ArcGIS


# Publications

## Selected Publications

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_articles}
:::
\endgroup

## Preprints

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
::: {#refs_preprints}
:::
\endgroup

## Book Chapters

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_books}
:::
\endgroup

## Reports

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_reports}
:::
\endgroup

# Grants

```{r grant}
readr::read_csv("data/grant.csv") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(with, when, what, where, why)
```

# Awards and Honours

```{r award}
readr::read_csv("data/award.csv") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Invited Guest Lectures

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

`r knitr::knit_child("data/invited.txt")`

\endgroup

# Papers and Posters Presented

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_proceedings}
:::
\endgroup

# Campus or Departmental Talks

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

`r knitr::knit_child("data/campus_talks.txt")`

\endgroup

# Extension and Community Outreach

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_extension}
:::
\endgroup

# Teaching Experience

## Classroom

```{r teaching}
readr::read_csv("data/teaching.csv") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

## Workshops

```{r workshop}
readr::read_csv("data/workshop.csv") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Service

```{r service, eval = TRUE}
readr::read_csv("data/service.csv") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Certifications

```{r certification, eval = TRUE}
readr::read_csv("data/certification.csv") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# Memberships

```{r membership, eval = TRUE}
readr::read_csv("data/membership.csv") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

<!-- *`r Sys.Date()`* -->
